---
title: "Network Analysis - Grey’s Anatomy Network of Romance"
output: html_document
---
```{r, echo=FALSE, cache=FALSE}
options(width = 200)
```
___
#### *Authors:* Ronit Yoari & Orel Swisa  
#### *Date*: May 3, 2016  
#### *The Dataset [Source](http://www.babelgraph.org/data/ga_edgelist.csv)*   
___
## *Data Description*
### *Vertices*
```{r, echo=FALSE, message=FALSE}
library("downloader")

folder<-".\\data\\ga_edgelist.csv"
if(!file.exists(folder)){
  # Download a csv file from the Internet:
  fileURL <- "http://www.babelgraph.org/data/ga_edgelist.csv"
  download.file(fileURL, destfile = folder)
  # Always record the date
  dateDownloaded <- date()
  dateDownloaded
}
library(igraph)
# Read from local drive
ga.data <- read.csv(folder,header=T)
g <- graph.data.frame(ga.data,directed=FALSE)
V(g)$name
```
### *Edges*
```{r,echo=FALSE, message=FALSE}
E(g)
```
### *Summary*
```{r,echo=FALSE,warning=FALSE,message=FALSE}
summary(g)
```
___
## *Centrality*
___
### *i. Betweeness* 
```{r,echo=FALSE}
btw <- betweenness(g) 
# rescale values to match the elements of a color vector 
btw.score <- round( (btw - min(btw)) * length(btw) / max(btw) ) + 1 
# create color vector, use rev to make red "hot" 
btw.colors <- rev(heat.colors(max(btw.score))) 
V(g)$color <- btw.colors[ btw.score ] 
g$layout <- layout.fruchterman.reingold(g)
plot(g)
which.max(btw)
max(btw)
```
___
### *ii. Closeness* 
```{r,echo=FALSE}
clo <- closeness(g) 
# rescale values to match the elements of a color vector 
clo.score <- round( (clo - min(clo)) * length(clo) / max(clo) ) + 1 
# create color vector, use rev to make red "hot" 
clo.colors <- rev(heat.colors(max(clo.score))) 
V(g)$color <- clo.colors[ clo.score ] 
plot(g)
which.max(clo)
max(clo)
```
___
### *iii. Eigencetor*
```{r,echo=FALSE}
temp <- eigen_centrality(g) 
evc<-temp$vector
# rescale values to match the elements of a color vector 
evc.score <- round( (evc - min(evc)) * length(evc) / max(evc) ) + 1 
# create color vector, use rev to make red "hot" 
evc.colors <- rev(heat.colors(max(evc.score))) 
V(g)$color <- evc.colors[ evc.score ] 
plot(g)
which.max(evc)
max(evc)
```
___
## *Identifying communities*
___
```{r,echo=FALSE,message=FALSE}
# Remove self-loops is exist
greyAnatomy <- simplify(g)
# Set seed (for layout) - so it won't be randomal
set.seed(200)
```
### *i. Zachary's algorithm*  
#### *The graph shown below describes the distribution of vertices communities, by color depending, according to **Zachary's algorithm***  
```{r,echo=FALSE,warning=FALSE,message=FALSE}
# Community strucure via short random walks
fc <- walktrap.community(greyAnatomy)
memb<-membership(fc)
lay <- layout.fruchterman.reingold(greyAnatomy)
plot(greyAnatomy, layout=lay, vertex.size=5, vertex.label=NA, vertex.color=memb+1, asp=FALSE)
```
  
#### *The number of the communities according to **Zachary's algorithm** is:* 
```{r,echo=FALSE,warning=FALSE,message=FALSE}
max(memb)
```
#### *The graph below shows the **distribution** of members in communities*
```{r,echo=FALSE,warning=FALSE,message=FALSE}
membTable <- table(memb)
barplot(membTable, col=terrain.colors(7) , main="Bar plot for Number of Members\nVS\nCommunity", 
  	xlab="#Community", ylab = "Number of Members")
memb
```
  
#### *Modularity*
```{r,echo=FALSE,warning=FALSE,message=FALSE}
fc$modularity
```
#### *Which one had the max modularity?*
```{r,echo=FALSE,warning=FALSE,message=FALSE}
# get the max modularity for this graph:
which.max(fc$modularity)
```
#### *What the value of the max modularity?*
```{r,echo=FALSE,warning=FALSE,message=FALSE}
max(fc$modularity)
```
___
### *ii. Second Algorithm - Girvan-Newman community detection algorithm*  
#### *The graph shown below describes the distribution of vertices communities, by color depending, according to **Girvan-Newman algorithm***  
```{r,echo=FALSE,warning=FALSE,message=FALSE}
fc <- edge.betweenness.community(greyAnatomy)
memb<-membership(fc)
plot(greyAnatomy, layout=lay, vertex.size=5, vertex.label=NA, vertex.color=memb+1, asp=FALSE)
```
  
#### *The number of the communities according to **Girvan-Newman** is:* 
```{r,echo=FALSE,warning=FALSE,message=FALSE}
max(memb)
```
#### *The graph below shows the **distribution** of members in communities*
```{r,echo=FALSE,warning=FALSE,message=FALSE}
membTable <- table(memb)
barplot(membTable, col=terrain.colors(7) , main="Bar plot for Number of Members\nVS\nCommunity", 
  	xlab="#Community", ylab = "Number of Members")
memb
```  
#### *Modularity*
```{r,echo=FALSE,warning=FALSE,message=FALSE}
fc$modularity
```
#### *Which one had the max modularity?*
```{r,echo=FALSE,warning=FALSE,message=FALSE}
# get the max modularity for this graph:
which.max(fc$modularity)
```
#### *What the value of the max modularity?*
```{r,echo=FALSE,warning=FALSE,message=FALSE}
max(fc$modularity)
```